---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# niceFunction

<!-- badges: start -->
[![R-CMD-check](https://github.com/tengku-hanis/niceFunction/workflows/R-CMD-check/badge.svg)](https://github.com/tengku-hanis/niceFunction/actions)
<!-- badges: end -->

The goal of niceFunction is to retain all random function that I found all over the books, forums, etc

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tengku-hanis/niceFunction")
```
## Example

This is a summary example which shows the use of each function. As of now, this package only have 6 functions:

1. histWithCurve
2. histCurve
3. histNA_byVar
4. regDiag
5. read_excel_allsheets
6. changeType

```{r example}
library(niceFunction)
```

histWithCurve give a histogram with a normal density curve
```{r histWithCurve}
histWithCurve(iris$Sepal.Length)
```

histCurve give a ggplot2 histogram with a normal desnity curve
```{r}
histCurve(iris, Sepal.Length)
```

histNA_byVar assess the distribution of NAs of certain variable is affected by another variable
```{r}
dat <- iris
dat[dat$Species == "setosa", "Sepal.Length"] <- NA
histNA_byVar(dat, Sepal.Length, Sepal.Width)
#indicate right-tailed missingness
```


regDiag is used for screening of outliers and influential cases
```{r regdiag}
mod <- lm(Sepal.Length ~ Species + Sepal.Width, data = iris)
regDiag(mod)
```

read_excel_allsheets read all excel sheets or several excel sheets
```{r read_excel_allsheets}
## Read all excel sheets (not run)
# read_excel_allsheets("datasets")

## Read several excel sheets (not run)
# read_excel_allsheets("datasets", pages = 2:5)
```

changeType change the variable type across list of data frames
```{r changeType, warning=FALSE}
# Make a list
iris_list <- list(iris1 = iris, iris2 = iris)

# Change one variable type
iris_list <- lapply(iris_list, changeType, Var = "Sepal.Width", funct = "as.character")

# Change 2 variables type
iris_list <- lapply(iris_list, changeType, Var = c("Sepal.Length", "Species"), funct = "as.character")
```


